Compute EVI mean trends

### 2017-11-20 analysis/evi/compute_MannKendall_evimean.Rmd
modify size

---
title: "Compute EVI mean trends"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Aug"
output:  
  md_document:
    variant: markdown_github
---
```{r, echo=FALSE, message=FALSE}
require(knitr)
opts_chunk$set(fig.align='center', fig.width = 14, message = FALSE, warning = FALSE) 
```

>>>>

---
title: "Compute EVI mean trends"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Aug"
output:  
  md_document:
    variant: markdown_github
---
```{r, echo=FALSE, message=FALSE}
require(knitr)
opts_chunk$set(message = FALSE, warning = FALSE) 
```
